---
title: "ccu18"
output: html_notebook
---

**Setup**

Working Directory
```{r setup}
knitr::opts_knit$set(root.dir = "C:/Users/Harrison Kirby/Desktop/GLP/CCU18")
```

Libraries
```{r libraries, message = FALSE}
library(lubridate)
library(ggthemes)
library(classInt)
library(showtext)
library(feather)
library(survey)
library(tidyverse)
library(magrittr)
library(reshape2)
```

Add functions
```{r}
insurance_time <- function(starting.year=2006){
  wd <- getwd()
  directory <- "Health/sahie_2008/"
  file_names <- list.files(directory)
  n<-length(file_names)
  y<-starting.year
  for (i in 1:n){
    file_path <- paste(directory, file_names[i], sep = "")
    data<-read_csv(file_path, skip=79)
    
    if(y > 2007){ data <- data %>% select(-X26) }
    
    data$statefips <- as.character(data$statefips)
    data$countyfips <- as.character(data$countyfips)
    
    data$statefips <- if_else( nchar(data$statefips) < 2, paste0("0",data$statefips), data$statefips)
    data$countyfips <- if_else( nchar(data$countyfips) < 3, paste0("0",data$countyfips), data$countyfips)
    data$countyfips <- if_else( nchar(data$countyfips) < 3, paste0("0",data$countyfips), data$countyfips)
    
    data$FIPS <- as.numeric(paste0(data$statefips, data$countyfips))
    all.peers <-subset(data, data$FIPS == 1073 |data$FIPS == 37119
                       |data$FIPS == 39061 |data$FIPS == 39049
                       |data$FIPS == 26081 |data$FIPS == 37081
                       |data$FIPS == 45045 |data$FIPS == 18097
                       |data$FIPS == 29095 |data$FIPS == 47093
                       |data$FIPS == 21111 |data$FIPS == 47157
                       |data$FIPS == 47037 |data$FIPS == 40109
                       |data$FIPS == 31055 |data$FIPS == 29189
                       |data$FIPS == 29510
                       |data$FIPS == 40143 |data$FIPS == 39113
                       |data$FIPS == 12031 |data$FIPS == 37183
                       |data$FIPS == 51760)
    
    all.peers$year<-y
    y<-y+1
    
    if(i==1){
     df<-all.peers 
    }
    else{
      names(all.peers)<-names(df)
      df<-rbind(df, all.peers)
    }
  }
  df
}


pull_peers_MSA<-function(data){
  all.peers <- filter(data, data$MSA %in% c("24340", "41180", "36420", "46140", "24860", "28940", "13820", "26900", "31140", "28140", "36540", "24660", "16740", "18140", "17140", "34980", "32820", "27260", "39580", "19380", "40060"))
  
  all.peers$baseline <- 1
  all.peers$current  <- 1
  
  all.peers$baseline[all.peers$MSA == 24340 | all.peers$MSA == 41180
                     |all.peers$MSA == 36420 | all.peers$MSA == 46140
                     |all.peers$MSA == 24860 | all.peers$MSA == 28940] <-0
  
  all.peers$current[all.peers$MSA == 27260 | all.peers$MSA == 39580
                    |all.peers$MSA == 19380 | all.peers$MSA == 40060] <-0
  all.peers
}

pull_peers_FIPS <- function(dat){
  all.peers <- subset(dat, dat$FIPS == 1073 | dat$FIPS == 37119
                      |dat$FIPS == 39061 |dat$FIPS == 39049
                      |dat$FIPS == 26081 |dat$FIPS == 37081
                      |dat$FIPS == 45045 |dat$FIPS == 18097
                      |dat$FIPS == 29095 |dat$FIPS == 47093
                      |dat$FIPS == 21111 |dat$FIPS == 47157
                      |dat$FIPS == 47037 |dat$FIPS == 40109
                      |dat$FIPS == 31055 |dat$FIPS == 29189
                      |dat$FIPS == 29510 |dat$FIPS == 40143
                      |dat$FIPS == 12031 |dat$FIPS == 37183
                      |dat$FIPS == 39113 |dat$FIPS == 51760
                      |dat$FIPS == "01073" | dat$FIPS == "MERGED")
  all.peers$baseline <- 1
  all.peers$current <- 1
  all.peers$baseline[all.peers$FIPS==26081|all.peers$FIPS==29189
                     |all.peers$FIPS==29510|all.peers$FIPS==40109
                     |all.peers$FIPS==40143|all.peers$FIPS==45045
                     |all.peers$FIPS==47093|all.peers$FIPS=="MERGED"]<-0
  all.peers$current[all.peers$FIPS== 12031|all.peers$FIPS==37183|
                      all.peers$FIPS==39113|all.peers$FIPS==51760]<-0
  all.peers
}
```

**Health Insurance Data**
```{r, messsage = FALSE, eval = FALSE}
data <- insurance_time()

hie_06_15 <- data %>%
  filter(agecat == 0) %>%
  filter(racecat == 0) %>%
  filter(sexcat == 0) %>%
  filter(iprcat == 0) %>%
  select(FIPS, year, PCTELIG)

data <- read_fwf("Health/sahie_2005/sahie-2005.txt", 
                 fwf_cols(statefips = c(1,2), countyfips = c(4,6), geocat = c(8,9), 
                          agecat = c(11,11), racecat = c(13,13), sexcat = c(15,15), iprcat = c(17,17), 
                          pop = c(19, 26), nic = c(28, 35), nic_moe = c(37, 44), nui = c(46, 53),
                          nui_moe = c(55, 62), PCTELIG = c(64, 67), pctelig_moe = c(69,73)),
                 col_types = cols("statefips" = col_character(), countyfips = col_character()),
                 skip = 41)

data$statefips <- if_else( nchar(data$statefips) < 2, paste0("0",data$statefips), data$statefips)
data$countyfips <- if_else( nchar(data$countyfips) < 3, paste0("0",data$countyfips), data$countyfips)
data$countyfips <- if_else( nchar(data$countyfips) < 3, paste0("0",data$countyfips), data$countyfips)

hie_05 <- data %>%
  mutate(FIPS = as.numeric(paste0(statefips, countyfips)),
         year = 2005) %>%
  filter(agecat == 0) %>%
  filter(racecat == 0) %>%
  filter(sexcat == 0) %>%
  filter(iprcat == 0) %>%
  select(FIPS, year, PCTELIG)

hie_05 <- subset(hie_05, hie_05$FIPS == 1073 | hie_05$FIPS == 37119
                  |hie_05$FIPS == 39061 |hie_05$FIPS == 39049
                  |hie_05$FIPS == 26081 |hie_05$FIPS == 37081
                  |hie_05$FIPS == 45045 |hie_05$FIPS == 18097
                  |hie_05$FIPS == 29095 |hie_05$FIPS == 47093
                  |hie_05$FIPS == 21111 |hie_05$FIPS == 47157
                  |hie_05$FIPS == 47037 |hie_05$FIPS == 40109
                  |hie_05$FIPS == 31055 |hie_05$FIPS == 29189
                  |hie_05$FIPS == 29510 |hie_05$FIPS == 40143
                  |hie_05$FIPS == 12031 |hie_05$FIPS == 37183
                  |hie_05$FIPS == 39113 |hie_05$FIPS == 51760
                  | hie_05$FIPS == "01073")

hie <- rbind(hie_06_15, hie_05)

hie$FIPS <- as.character(hie$FIPS)
hie$year <- as.character(hie$year)
```

**Read ACS data**

Read in data and construct counties from PUMAs. PUMAs are identified using State FIPS codes and PUMA numbers. PUMAs boundaries were redrawn in 2012 based on the 2010 census, so 
```{r}
acs <- read_feather("C:/Users/Harrison Kirby/Desktop/GLP/ccu17_beyond_poverty/data/all_obs.feather")

acs$FIPS <- NA
#PUMAs from 2005-2011
acs$FIPS[acs$STATEFIP == 1 & (acs$YEAR < 2012 & acs$PUMA %in% c(901, 905, 902, 903, 904))] <- 1073
acs$FIPS[acs$STATEFIP == 12 & (acs$YEAR < 2012 & acs$PUMA %in% c(1106, 1105, 1103, 1104, 1102, 1107))] <- 12031
acs$FIPS[acs$STATEFIP == 18 & (acs$YEAR < 2012 & acs$PUMA %in% c(2303, 2302, 2301, 2307, 2306, 2304, 2305))] <- 18097
acs$FIPS[acs$STATEFIP == 21 & (acs$YEAR < 2012 & acs$PUMA %in% c(1702, 1704, 1705, 1701, 1703))] <- 21111
acs$FIPS[acs$STATEFIP == 26 & (acs$YEAR < 2012 & acs$PUMA %in% c(1402, 1403, 1401, 1300))] <- 26081
acs$FIPS[acs$STATEFIP == 29 & (acs$YEAR < 2012 & acs$PUMA %in% c(1004, 1002, 1100, 1003, 902, 901))] <- 29095
acs$FIPS[acs$STATEFIP == 29 & (acs$YEAR < 2012 & acs$PUMA %in% c(1704, 1706, 1703, 1705, 1708, 1701, 1702, 1707))] <- 29189
acs$FIPS[acs$STATEFIP == 29 & (acs$YEAR < 2012 & acs$PUMA %in% c(1802, 1801, 1803))] <- 29510
acs$FIPS[acs$STATEFIP == 31 & (acs$YEAR < 2012 & acs$PUMA %in% c(903, 904, 902, 901))] <- 31055
acs$FIPS[acs$STATEFIP == 37 & (acs$YEAR < 2012 & acs$PUMA %in% c(1601, 1602, 1700))] <- 37081
acs$FIPS[acs$STATEFIP == 37 & (acs$YEAR < 2012 & acs$PUMA %in% c(901, 904, 902, 903, 905, 1000))] <- 37119
acs$FIPS[acs$STATEFIP == 37 & (acs$YEAR < 2012 & acs$PUMA %in% c(2701, 2703, 2702, 2602, 2601))] <- 37183
acs$FIPS[acs$STATEFIP == 39 & (acs$YEAR < 2012 & acs$PUMA %in% c(3107, 3101, 3103, 3109, 3106, 3108, 3102, 3104, 3105))] <- 39049
acs$FIPS[acs$STATEFIP == 39 & (acs$YEAR < 2012 & acs$PUMA %in% c(4503, 4502, 4401, 4404, 4501, 4403, 4402))] <- 39061
acs$FIPS[acs$STATEFIP == 39 & (acs$YEAR < 2012 & acs$PUMA %in% c(4102, 4101, 4103, 4000))] <- 39113
acs$FIPS[acs$STATEFIP == 40 & (acs$YEAR < 2012 & acs$PUMA %in% c(1400, 1302, 1301))] <- 40109
acs$FIPS[acs$STATEFIP == 40 & (acs$YEAR < 2012 & acs$PUMA %in% c(1200, 1100))] <- 40143
acs$FIPS[acs$STATEFIP == 45 & (acs$YEAR < 2012 & acs$PUMA %in% c(202, 201))] <- 45045
acs$FIPS[acs$STATEFIP == 47 & (acs$YEAR < 2012 & acs$PUMA %in% c(2202, 2205, 2204, 2201, 2203))] <- 47037
acs$FIPS[acs$STATEFIP == 47 & (acs$YEAR < 2012 & acs$PUMA %in% c(1400, 1301))] <- 47093
acs$FIPS[acs$STATEFIP == 47 & (acs$YEAR < 2012 & acs$PUMA %in% c(3202, 3105, 3104, 3103, 3102, 3201, 3101))] <- 47157
acs$FIPS[acs$STATEFIP == 51 & (acs$YEAR < 2012 & acs$PUMA %in% c(1200))] <- 51760

#PUMAs from 2012 and after
acs$FIPS[acs$STATEFIP == 1 & (acs$YEAR > 2011 & acs$PUMA %in% c(1301, 1302, 1303, 1304, 1305))] <- 1073
acs$FIPS[acs$STATEFIP == 12 & (acs$YEAR > 2011 & acs$PUMA %in% c(3101, 3102, 3103, 3104, 3105, 3106, 3107))] <- 12031
acs$FIPS[acs$STATEFIP == 18 & (acs$YEAR > 2011 & acs$PUMA %in% c(2301, 2302, 2303, 2304, 2305, 2306, 2307))] <- 18097
acs$FIPS[acs$STATEFIP == 21 & (acs$YEAR > 2011 & acs$PUMA %in% c(1701, 1702, 1703, 1704, 1705, 1706))] <- 21111
acs$FIPS[acs$STATEFIP == 26 & (acs$YEAR > 2011 & acs$PUMA %in% c(1001, 1002, 1003, 1004))] <- 26081
acs$FIPS[acs$STATEFIP == 29 & (acs$YEAR > 2011 & acs$PUMA %in% c(1001, 1002, 1003, 1004, 1005))] <- 29095
acs$FIPS[acs$STATEFIP == 29 & (acs$YEAR > 2011 & acs$PUMA %in% c(1801, 1802, 1803, 1804, 1805, 1806, 1807, 1808))] <- 29189
acs$FIPS[acs$STATEFIP == 29 & (acs$YEAR > 2011 & acs$PUMA %in% c(1901, 1902))] <- 29510
acs$FIPS[acs$STATEFIP == 31 & (acs$YEAR > 2011 & acs$PUMA %in% c(901, 902, 903, 904))] <- 31055
acs$FIPS[acs$STATEFIP == 37 & (acs$YEAR > 2011 & acs$PUMA %in% c(1701, 1702, 1703, 1704))] <- 37081
acs$FIPS[acs$STATEFIP == 37 & (acs$YEAR > 2011 & acs$PUMA %in% c(3101, 3102, 3103, 3104, 3105, 3106, 3107, 3108))] <- 37119
acs$FIPS[acs$STATEFIP == 37 & (acs$YEAR > 2011 & acs$PUMA %in% c(1201, 1202, 1203, 1204, 1205, 1206, 1207, 1208))] <- 37183
acs$FIPS[acs$STATEFIP == 39 & (acs$YEAR > 2011 & acs$PUMA %in% c(4101, 4102, 4103, 4104, 4105, 4106, 4107, 4108, 4109, 4110, 4111))] <- 39049
acs$FIPS[acs$STATEFIP == 39 & (acs$YEAR > 2011 & acs$PUMA %in% c(5501, 5502, 5503, 5504, 5505, 5506, 5507))] <- 39061
acs$FIPS[acs$STATEFIP == 39 & (acs$YEAR > 2011 & acs$PUMA %in% c(4601, 4602, 4603, 4604))] <- 39113
acs$FIPS[acs$STATEFIP == 40 & (acs$YEAR > 2011 & acs$PUMA %in% c(1001, 1002, 1003, 1004, 1005, 1006))] <- 40109
acs$FIPS[acs$STATEFIP == 40 & (acs$YEAR > 2011 & acs$PUMA %in% c(1201, 1202, 1203))] <- 40143
acs$FIPS[acs$STATEFIP == 45 & (acs$YEAR > 2011 & acs$PUMA %in% c(102, 103, 104, 105))] <- 45045
acs$FIPS[acs$STATEFIP == 47 & (acs$YEAR > 2011 & acs$PUMA %in% c(2501, 2502, 2503, 2504, 2505))] <- 47037
acs$FIPS[acs$STATEFIP == 47 & (acs$YEAR > 2011 & acs$PUMA %in% c(1602, 1603, 1604))] <- 47093
acs$FIPS[acs$STATEFIP == 47 & (acs$YEAR > 2011 & acs$PUMA %in% c(3201, 3202, 3203, 3204, 3205, 3206, 3207, 3208))] <- 47157
acs$FIPS[acs$STATEFIP == 51 & (acs$YEAR > 2011 & acs$PUMA %in% c(51235))] <- 51760
```

Subset data to peer and exclude group quarters residents. Add recognizable city names.
```{r}
acs <- pull_peers_FIPS(acs)
acs <- acs %>% filter(GQ == 1 | GQ == 2)

acs$FIPS[acs$FIPS == 29189] = 'MERGED'
acs$FIPS[acs$FIPS == 29510] = 'MERGED'

acs$city <- NA
acs$city[acs$FIPS == 1073]  = 'Birmingham'
acs$city[acs$FIPS == 12031] = 'Jacksonville'
acs$city[acs$FIPS == 18097] = 'Indianapolis'
acs$city[acs$FIPS == 21111] = 'Louisville'
acs$city[acs$FIPS == 26081] = 'Grand Rapids'
acs$city[acs$FIPS == 29095] = 'Kansas City'
acs$city[acs$FIPS == 'MERGED'] = 'St. Louis'
acs$city[acs$FIPS == 31055] = 'Omaha'
acs$city[acs$FIPS == 37081] = 'Greensboro'
acs$city[acs$FIPS == 37119] = 'Charlotte'
acs$city[acs$FIPS == 37183] = 'Raleigh'
acs$city[acs$FIPS == 39049] = 'Columbus'
acs$city[acs$FIPS == 39061] = 'Cincinnati'
acs$city[acs$FIPS == 39113] = 'Dayton'
acs$city[acs$FIPS == 40109] = 'Oklahoma City'
acs$city[acs$FIPS == 40143] = 'Tulsa'
acs$city[acs$FIPS == 45045] = 'Greenville'
acs$city[acs$FIPS == 47037] = 'Nashville'
acs$city[acs$FIPS == 47093] = 'Knoxville'
acs$city[acs$FIPS == 47157] = 'Memphis'
acs$city[acs$FIPS == 51760] = 'Richmond'
```

Race
```{r}
acs$race <- NA
acs$race[acs$RACE == 1 & acs$HISPAN == 0] <- 0
acs$race[acs$RACE == 2 & acs$HISPAN == 0] <- 1
acs$race[acs$HISPAN == 1] <- 2
```

**Create variables**

*Education*

Poverty and child poverty
```{r}
acs %<>%
  mutate(pov = if_else(POVERTY <= 100, 1, 0),
         pov = replace(pov, POVERTY == 1, 0))
```

Degree Attainment and Young Adult Degree Attainment
```{r}
educ_replace <- function(x) {replace(x, acs$EDUCD %in% c(0, 1, 999), NA)}

acs %<>%
  mutate(nohs = if_else(EDUC <= 61, 1, 0),
         hs = if_else(EDUCD %in% c(62, 63, 64), 1, 0),
         somecol = if_else(EDUCD %in% c(70, 71, 80, 90, 100, 110, 111, 112, 113), 1, 0),
         assoc = if_else(EDUCD %in% c(81, 82, 83), 1, 0),
         assoc_plus = if_else(EDUCD > 80, 1, 0),
         bach = if_else(EDUCD == 101, 1, 0),
         bach_plus = if_else(EDUCD > 100, 1, 0),
         grad = if_else(EDUCD > 114, 1, 0)) %>%
  map_at(c('nohs', 'hs', 'somecol', 'assoc', 'assoc_plus', 'bach', 'bach_plus', 'grad'), educ_replace) %>%
  as.data.frame()
```

High Wage Occupations

*Jobs*

Working poverty
```{r}
#generate employment variable at the household level
acs %<>%
  mutate(emp = if_else(EMPSTAT == 1, 1, 0),
         emp = replace(emp, EMPSTAT == 0, NA)) %>%
  group_by(SERIAL, YEAR) %>%
  mutate(fam_emp = if_else(any(emp == 1, na.rm = TRUE), 1, 0)) %>%
  ungroup()

#generate working poverty variable
acs %<>%
  mutate(working_poverty = if_else(fam_emp == 1 & pov == 1, 1, 0))
```

Transit

Median Earnings

Personal Income Per Capita

Median Household Incomem

Unemployment
```{r}
acs %<>%
  mutate(unemp = if_else(EMPSTAT == 2, 1, 0))

acs$unemp[acs$EMPSTAT == 0] <- NA
acs$unemp[acs$EMPSTAT == 3] <- NA
```

*Quality of Place*

Burdened Households
```{r}
acs %<>%
  mutate(OWNCOST = replace(OWNCOST, OWNCOST == 99999, NA),
         FTOTINC = replace(FTOTINC, FTOTINC == 99999, NA),
         hcost   = max(OWNCOST, FTOTINC, na.rm = TRUE),
         hcost_burdened = if_else(hcost*12/FTOTINC > .5, 1, 0))

#mpi_msa$hcost_burdened[is.na(mpi_msa$hcost_burdened)] <- 0
```

Disconnected Youth
```{r, eval = FALSE}
acs %<>%
  mutate(
    in_school = if_else(SCHOOL == 2, 1, 0),
    in_school = replace(in_school, SCHOOL == 0 | SCHOOL == 9, NA),
    disconnected_youth = if_else(in_school == 0 & emp == 0, 1, 0))
```

Homeownership

Commute Time


**Create output**
```{r}
survey_df <- svydesign(ids = ~1, weights = ~PERWT, data = acs)

svy_child <- survey_df %>% subset(AGE < 18)
svy_young_child <- survey_df %>% subset(AGE < 5)
svy_df_old_child <- survey_df %>% subset(AGE >= 5 & AGE <= 17)

svy_25_34 <- survey_df %>% subset(AGE >= 25 & AGE <= 34)
svy_25_64 <- survey_df %>% subset(AGE >= 25 & AGE <= 64)

acs_hhold <- acs[!duplicated(acs[c('YEAR', 'SERIAL')]),]
survey_df_hhold <- svydesign(ids = ~1, weights = ~HHWT, data = acs_hhold)

#results <- svyby(~assoc_plus + bach_plus + grad + unemp + working_poverty, ~FIPS+YEAR+race, design = survey_df, svymean, na.rm = TRUE)

results <- svyby(~bach_plus, ~FIPS+YEAR+race, design = survey_df, svymean, na.rm = TRUE)


output <- results %>%
  select(FIPS, race, year = YEAR, bach_plus) %>%
  mutate_at(vars(bach_plus), function(x) {x * 100}) %>%
  {
    x <- .
    full_join(
      x %>% 
        filter(race == 0) %>% 
        select(-race) %>%
        rename(bach_w = bach_plus),
      x %>% 
        filter(race == 2) %>%
        select(-race) %>%
        rename(bach_b = bach_plus),
      by = c('FIPS', 'year'))
  }
```

```{r, eval = FALSE}

output <- results %>%
  select(FIPS, race, year = YEAR, assoc_plus, bach_plus, grad, unemp, working_poverty) %>%
  mutate_at(vars(assoc_plus, bach_plus, grad, unemp, working_poverty), function(x) {x * 100}) %>%
  {
    x <- .
    full_join(
      x %>% 
        filter(race == 0) %>% 
        select(-race) %>%
        rename(assoc_w = assoc,
               unemp_w = unemp,
               bach_w = bach),
      x %>% 
        filter(race == 1) %>%
        select(-race) %>%
        rename(assoc_b = assoc,
               unemp_b = unemp,
               bach_b = bach),
      by = c('FIPS', 'year'))
  }
```

```{r}
output %<>% pull_peers_FIPS()

output$city <- NA
output$city[output$FIPS == 1073]  = 'Birmingham'
output$city[output$FIPS == 12031] = 'Jacksonville'
output$city[output$FIPS == 18097] = 'Indianapolis'
output$city[output$FIPS == 21111] = 'Louisville'
output$city[output$FIPS == 26081] = 'Grand Rapids'
output$city[output$FIPS == 29095] = 'Kansas City'
output$city[output$FIPS == 'MERGED'] = 'St. Louis'
output$city[output$FIPS == 31055] = 'Omaha'
output$city[output$FIPS == 37081] = 'Greensboro'
output$city[output$FIPS == 37119] = 'Charlotte'
output$city[output$FIPS == 37183] = 'Raleigh'
output$city[output$FIPS == 39049] = 'Columbus'
output$city[output$FIPS == 39061] = 'Cincinnati'
output$city[output$FIPS == 39113] = 'Dayton'
output$city[output$FIPS == 40109] = 'Oklahoma City'
output$city[output$FIPS == 40143] = 'Tulsa'
output$city[output$FIPS == 45045] = 'Greenville'
output$city[output$FIPS == 47037] = 'Nashville'
output$city[output$FIPS == 47093] = 'Knoxville'
output$city[output$FIPS == 47157] = 'Memphis'
output$city[output$FIPS == 51760] = 'Richmond'
  
```

**Graph data**

```{r}
source('C:/Users/Harrison Kirby/Desktop/GLP/glp_website/graphing_functions.R')
font_add("Museo Sans 300", "MuseoSans_300.otf")
font_add("Museo Sans 300 Italic", "MuseoSans_300_Italic.otf")
```

```{r}
setwd('Images')

png("associates_white.png", 900, 600, res = 100, type = "cairo")
graph_trendline(output, 
                "assoc_w",
                plot_title = "Associate Degrees or Higher, White, Ages 25-34",
                rollmean = 3,
                xmin = 2005,
                xmax = 2015,
                y_title = "Percent")
dev.off()

png("associates_black.png", 900, 600, res = 100, type = "cairo")
graph_trendline(output, 
                "assoc_b",
                plot_title = "Associate Degrees or Higher, Black, Ages 25-34",
                rollmean = 3,
                xmin = 2005,
                xmax = 2015,
                y_title = "Percent")
dev.off()

png("bach_white.png", 900, 600, res = 100, type = "cairo")
graph_trendline(output, 
                "bach_w",
                plot_title = "Bachelor's Degrees or Higher, White, Ages 25-34",
                rollmean = 3,
                xmin = 2005,
                xmax = 2015,
                y_title = "Percent")
dev.off()

png("bach_black.png", 900, 600, res = 100, type = "cairo")
graph_trendline(output, 
                "bach_b",
                plot_title = "Bachelor's Degrees or Higher, Hispanic, Ages 25-34",
                rollmean = 3,
                xmin = 2005,
                xmax = 2015,
                y_title = "Percent")
dev.off()

png("unemployment_white.png", 900, 600, res = 100, type = "cairo")
graph_trendline(output, 
                "unemp_w",
                plot_title = "Unemployment, White",
                rollmean = 3,
                xmin = 2005,
                xmax = 2015,
                y_title = "Percent")
dev.off()

png("unemployment_black.png", 900, 600, res = 100, type = "cairo")
graph_trendline(output, 
                "unemp_b",
                plot_title = "Unemployment, Black",
                rollmean = 3,
                xmin = 2005,
                xmax = 2015,
                y_title = "Percent")
dev.off()
```












